Prehensile Manipulation Planning: Modelling, Algorithms and Implementation

### 2020-11-05 ijrr.tex
Write conclusion and set doublespace mode.
Small improvements.
Add abstract.

\documentclass[Afour,sageh,times]{sagej}

@@

\begin{abstract}
\end{abstract}

\keywords{robotics, manipulation planning, constrained path planning,
  path planning}

>>>>

\documentclass[Afour,sageh,times,doublespace]{sagej}

@@

\begin{abstract}
  This paper presents a software platform taylored for prehensile manipulation
  planning named Humanoid Path Planner. The platform implements an original way
  of modelling manipulation planning through a constraint graph that represents
  the numerical constraints that define the manipulation problem. We propose an
  extension of RRT algorithm to manipulation planning that is able to solve a
  large variety of problems. We provide replicable experimental results via a
  docker image that readers may download to run the experimental results by
  themselves.
\end{abstract}

\keywords{robotics, manipulation planning, constrained path planning,
  path planning, software platform}
